Models of Lambek calculus with subexponentials

### 2019-06-24 PaperDraft.tex
updates in soundness

\begin{defin}
$ $
\begin{enumerate}
  \item A quantic conucleus is called central, if for all
  $a, b \in \mathcal{Q}, \Box a \cdot b = b \cdot \Box a$.

  \item A quantic conucleus is called strong square-increasing,
  if for all $a, b \in \mathcal{Q}, \Box a \cdot b \leq \Box a \cdot b \cdot \Box a$ and
  $b \cdot \Box a \leq \Box a \cdot b \cdot \Box a$.

@@

@@

\begin{lemma}
  $ $
  Let $\mathcal{Q}$ be a quantale. Let $I$, $I_1$, and $I_2$ be quantic conuclei. Thus, the following properties hold:
  \begin{enumerate}
  \item $I_1 a_1 \cdot I_2 a_2 \leq I (I_1 a_1 \cdot I_2 a_2)$, where $I_i \leq I, i = 1,2$.
  \item If $I$ is unital and weak idempotent, then $I$ is central.
  \item Let $S \subseteq \mathcal{Q}$ be a subquantale, then $I : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
  \item Let $S_1$ and $S_2$ are subquantales such that $mathcal{S}_1 \subseteq \mathcal{S}_2 \subseteq \mathcal{Q}$. Then $\Box_{\mathcal{S}_1} (a) \leq \Box_{\mathcal{S}_1} (a)$.
  \end{enumerate}
\end{lemma}

@@

  Hence, $b \cdot I a = I a \cdot b$, so for all $a \in \mathcal{Q}, I a \in \mathcal{Z}(\mathcal{Q})$.
  \item See Rosental.
  \item Immediately.
\end{enumerate}
\end{proof}

@@

  Let $\Sigma$ be a subexponential signature and $\sigma : \Sigma \to CN(\mathcal{Q})$ for a contravariant map
  $S : \Sigma \to Sub(\mathcal{Q})$, then:
  \begin{enumerate}
  \item For all $s_1, s_2 \in \Sigma$, if $s_1 \preceq s_2$, then $\sigma(s_2) \leq \sigma(s_1)$.
  In other words, $\sigma$ is a contravariant functor from $\Sigma$ to $Sub(\mathcal{Q})$.
  \item $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
  \item If $s \in \mathcal{W} \cap \mathcal{C}$, then $\sigma(s)$ is a central quantic conucleus.
\end{enumerate}
\end{lemma}

@@

  \begin{enumerate}
  \item Let $s_1, s_2 \in \Sigma$ and $s_1 \leq s_2$. Then $S(s_2) \subseteq S(s_1)$.
  So, $\forall a \in \mathcal{Q}, \bigvee \{ s \in S(s_2) \: | \: s \leq a \} \leq \bigvee \{ s \in S(s_1) \: | \: s \leq a \}$. Thus, $\sigma(s_2) \leq \sigma(s_1)$.
  \item Let $s_1 \in A$ and $s_1 \preceq s_2$. By the previous part, $\sigma(s_2) \leq \sigma(s_1)$. Suppose $\sigma(s_2) \notin \sigma(A)$, then $s_2 \notin A$. But $s_2 \in A$ so far as $A$ is upwardly closed. Contradiction.
  \item Let $s \in \mathcal{W} \cap \mathcal{C}$ and $a \in \mathcal{Q}$,
  then $\sigma(s)(a) = \bigvee \{ x \in S(s) \: | \: x \leq a, x \in \mathcal{Z}(\mathcal{Q}), \text{ and } \forall b \in \mathcal{Q}, (x \cdot b) \vee (b \cdot x) \leq x \cdot b \cdot x \}$. Thus, by Lemma, $\sigma(s)(a) \in \mathcal{Z}(\mathcal{Q})$.

>>>>

\begin{defin}
$ $
\begin{enumerate}
  \item A quantic conucleus $I$ is called central, if for all
  $a, b \in \mathcal{Q}, I a \cdot b = b \cdot I a$.

  \item A quantic conucleus is called strong square-increasing,
  if for all $a, b \in \mathcal{Q}, I a \cdot b \leq I a \cdot b \cdot I a$ and
  $b \cdot I a \leq I a \cdot b \cdot I a$.

@@

  \begin{enumerate}
    \item Let $S \subseteq \mathcal{Q}$ be a subquantale, then $I : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
    \item Let $S_1$ and $S_2$ are subquantales such that $\mathcal{S}_1 \subseteq \mathcal{S}_2 \subseteq \mathcal{Q}$. Then $I_{\mathcal{S}_1} (a) \leq I_{\mathcal{S}_1} (a)$, where $I_{\mathcal{S}_i}, i = 1,2$ are quantic conucleis defined according to the previous part.
  \end{enumerate}
\end{lemma}

\newpage

\begin{lemma} Let $I$ be a quantic conucleus, then for all $a \in \mathcal{Q}$, $I a = \bigvee \{ q \in Q_{I} \: | \: s \leq a \}$, where $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$.
\end{lemma}

So far as $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$ is a subquantale, then $I' a = \bigvee \{ q \in Q_{I} \: | \: s \leq a \}$ is a quantic conucleus. Let us show that these operations are equavalent.

From the one hand,

$\begin{array}{lll}
&\bigvee \{ q \in Q_{I} \: | \: s \leq a \} = & \\
& \:\:\:\:\:\:\:\: \text{$s \in Q_{I}$, so s is a fixpoint of $I$} & \\
&\bigvee \{ q \in Q_{I} \: | \: I s \leq a \} = & \\
& \:\:\:\:\:\:\:\: \text{By equivalence}& \\
&\bigvee \{ q \in Q_{I} \: | \: I s \leq I a \} = & \\
& \:\:\:\:\:\:\:\: \text{By fixpoint} & \\
&\bigvee \{ q \in Q_{I} \: | \: s \leq I a \} \leq I a& \\
\end{array}$

On the other hand, $I a \leq a$, then $I a \in \{ q \in Q_{I} \: | \: q \leq a \}$, so far as $I a \in Q_{I}$ (by idempotence). Thus, $I a \leq \bigvee \{ q \in Q_{I} \: | \: q \leq a \}$.

Let $I_1$ be a quantic conucleus $I_2$ a unital (central, strong weak increasing) quantic conucleus such that $I_1 \leq I_2$,
then $I_1$ is a unital (central, strong weak increasing).

\begin{enumerate}
  \item Let $a \in \mathcal{Q}$ (here $\mathcal{Q}$ is supposed to be a unital).
  Then $I_2 a \leq \varepsilon$, but $I_1 \leq I_2$, so $I_1 a \leq I_2 a$. By transitivity, $I_1 a \leq \varepsilon$.
  \item Let $a \in \mathcal{Q}$ and $I_2$ is a central quantic conucleus. Let $I_1$ be a quantic conucleus and $I_1 \leq I_2$.

  Thus, $I_2 a \in \mathcal{Z}(\mathcal{Q})$ and, obviously, $Q_{I_2} \subseteq \mathcal{Z}(\mathcal{Q})$.

  Let $b \in Q_{I_1}$, then $b = I_1 b \leq I_2 b \leq b$. Thus, $b = I_2 b$ and $b \in Q_{I_2}$. So, $Q_{I_1} \subseteq \mathcal{Z}(\mathcal{Q})$.

  Let us check that $I_1$ commutes with each other element $d \in \mathcal{Q}$

  $\begin{array}{lll}
  & I_1 a \cdot d = \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} \cdot d = & \\
  & \:\:\:\:\:\:\:\: \text{By quantale axiom}& \\
  & \bigvee \{ q \cdot d \: | \: q \in Q_{I_1} \: \& \: q \leq a \} = & \\
  & \:\:\:\:\:\:\:\: \text{As we proved, $q \in \mathcal{Z}(\mathcal{Q})$} & \\
  & \bigvee \{ d \cdot q \: | \: q \in Q_{I_1} \: \& \: q \leq a \} = & \\
  & \:\:\:\:\:\:\:\: \text{By quantale axiom}& \\
  & d \cdot \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} = & \\
  & \:\:\:\:\:\:\:\: \text{By Lemma \# n}& \\
  & d \cdot I_1 a &
  \end{array}$

  \item Let $I_2$ be a strong square increasing. Then, for all $a \in \mathcal{Q}$ and $b \in Q_{I_2}$,
  $a \cdot b \leq b \cdot a \cdot b$ and $b \cdot a \leq b \cdot a \cdot b$.

  Let $c \in Q_{I_1}$. Similarly to the previous part, $c = I_1 c \leq I_2 c \leq c$, then $c \in Q_{I_2}$ and
  $I_1$ is a strong square increasing.
\end{enumerate}
\end{proof}

@@

\begin{lemma}
  $ $
  Let $\mathcal{Q}$ be a quantale. Let $I$, $I_1$, and $I_2$ be quantic conuclei. Thus, the following properties hold:
  \begin{enumerate}
  \item $I_1 a_1 \cdot I_2 a_2 \leq I (I_1 a_1 \cdot I_2 a_2)$, where $I_i \leq I, i = 1,2$.
  \item If $I$ is unital and weak idempotent, then $I$ is central.
  \end{enumerate}
\end{lemma}

@@

  Hence, $b \cdot I a = I a \cdot b$, so for all $a \in \mathcal{Q}, I a \in \mathcal{Z}(\mathcal{Q})$.
\end{enumerate}
\end{proof}

@@

  \begin{enumerate}
    \item $s \in \mathcal{W}$, then $\sigma(s)$ is a unital modality.
    \item $s \in \mathcal{E}$, then $\sigma(s)$ is a central modality.
    \item $s \in \mathcal{C}$, then $\sigma(s)$ is GSI modality.
  \end{enumerate}
\end{lemma}

\begin{proof}
  By construction.
\end{proof}

\begin{lemma}
  Let $s_1 \in \mathcal{W}$ and $s_1 \preceq s_2$, then $\sigma(s_2)$ is a central modality.
\end{lemma}

\begin{proof}
\end{proof}

  Let $\Sigma$ be a subexponential signature and $\sigma : \Sigma \to CN(\mathcal{Q})$ for a contravariant map
  $S : \Sigma \to Sub(\mathcal{Q})$, then:
  \begin{enumerate}
  \item For all $s_1, s_2 \in \Sigma$, if $s_1 \preceq s_2$, then $\sigma(s_2) \leq \sigma(s_1)$.
  In other words, $\sigma$ is a contravariant functor from $\Sigma$ to $Sub(\mathcal{Q})$.
  $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
  \item If $s \in \mathcal{W} \cap \mathcal{C}$, then $\sigma(s)$ is a central quantic conucleus.
\end{enumerate}
\end{lemma}

@@

  \begin{enumerate}
  \item Let $s_1, s_2 \in \Sigma$ and $s_1 \leq s_2$. Then $S(s_2) \subseteq S(s_1)$.
  So, $\forall a \in \mathcal{Q}, \bigvee \{ s \in S(s_2) \: | \: s \leq a \} \leq \bigvee \{ s \in S(s_1) \: | \: s \leq a \}$. Thus, $\sigma(s_2) \leq \sigma(s_1)$.
  \item
  \item Let $s_1 \in A$ and $s_1 \preceq s_2$. By the previous part, $\sigma(s_2) \leq \sigma(s_1)$. Suppose $\sigma(s_2) \notin \sigma(A)$, then $s_2 \notin A$. But $s_2 \in A$ so far as $A$ is upwardly closed. Contradiction.
  \item Let $s \in \mathcal{W} \cap \mathcal{C}$ and $a \in \mathcal{Q}$,
  then $\sigma(s)(a) = \bigvee \{ x \in S(s) \: | \: x \leq a, x \leq \varepsilon, \text{ and } \forall b \in \mathcal{Q}, (x \cdot b) \vee (b \cdot x) \leq x \cdot b \cdot x \}$. Thus, by Lemma, $\sigma(s)(a) \in \mathcal{Z}(\mathcal{Q})$.
